Specification and Verification of Stencil Computation Shape

### 2016-11-15 paper.tex
abstract

>>>>

\begin{abstract}
Stencil computations are a common programming pattern in numerical
  code and typically form the core of graphics and scientific
  computing applications. However, they are often complex and
  unwieldy, involving substantial fine-grained manipulation of array
  indices across multiple arrays and dimensions. This requires careful
  testing, which is almost always done manually and then discarded
  during development. In this paper, we propose an alternate approach:
  a specification language and automated tool for verifying the
  spatial behaviour of stencils. The specification language is based
  on the hypothesis that stencil computations read from arrays with a
  regular, fixed pattern which can be captured abstractly by a simple
  set of combinators in our specification language. These
  specifications can be embedded as annotations in source code,
  against which code can be checked for conformance. For legacy code,
  spatial specifications can be inferred, providing documentation and
  aiding future software maintenance. We evaluate our language against
  a corpus of numerical Fortran code, and show that the vast majority
  of stencil computations indeed have a simple, regular, static shape
  validating the design of our language.  We introduce the
  language, checking, and inference procedures, and its evaluation.
\end{abstract}
